---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# triangdist

The triangdist package provides comprehensive statistical functions for calculating and simulating the triangular distribution in R. It includes tools for density (dtriang), cumulative distribution (ptriang), quantiles (qtriang), and random number generation (rtriang).

# Installation

You can install the development version of triangdist directly from GitHub using the devtools package:

```r
# install.packages("devtools")
devtools::install_github("yujingztd/triangdist")
```

# Examples of use

```{r}
library(triangdist)

# 1. Calculate the probability density function at the mode (x = 1)
dtriang(x = 1, min = 0, max = 3, mode = 1)

# 2. Generate 5 random values following this distribution
rtriang(n = 5, min = 0, max = 3, mode = 1)
```
